\thispagestyle{fancy}
\chapter{Introduction} \label{ch:introduction}
\section*{\centering Chapter \thechapter}
\section*{\centering Introduction}

\section{Introduction}

In recent years COVID-19 has become extremely widespread. It attacks the human respiratory system and leads to complicated respiratory problems. This disease can be very severe depending on a person's health and presence of comorbidities. Cardiovascular comorbidities are very common in severe cases of COVID-19 disease. Cardiovascular comorbidities are also harder to detect without proper equipment. One detection method is to check the presence of arrhythmia in patients. Arrhythmia is improper beating of the heart, whether irregular, too fast or too slow. This can be detected by reading ECG signals.  As COVID-19 has put a lot of stress on the medical staff so detection is taking more time than usual.   Increased access to the Internet has led various industries to implement machine learning and AI for  service. This leads to the growth of research in the field of machine learning and will affect machine learning in various fields. The medical and healthcare industries are one of them. Machine learning is  used to quickly detect a patient's illness and classify viruses and other microbes. Machine learning algorithms have already proven to be very effective in medical applications.

The reading of these ECG signals and detection can be done with help of the machine learning system. The supervised learning algorithms can be used for detection of these symptoms in a much faster and more efficient way. The supervised algorithms are already proven faster in such precise classification tasks than unsupervised algorithms. Once trained this algorithm can be used for future predictions too.

There are multiple supervised algorithms available, so we can choose algorithms that suit our needs. In case of the general populace this step can be automated. The preset of a few algorithms can be provided to the system, then the machine can train and select the best model selected for the provided dataset. This will allow medical staff to focus on patient care and develop solutions to medical problems.

\section{Motivation} \label{sec:motivation}

COVID-19 disease is a global pandemic which caused more than 250 million infections world-wide and 5 million deaths. Followed by respiratory disorders, the cardiovascular diseases and cardiovascular complications lead to the most severe cases and are one of most common causes of deaths in COVID-19 patients. Due to the nature of cardiovascular disease they often go undetected and untreated. This further leads to risks of severe COVID-19 in those individuals.

Earlier diagnosis of cardiovascular disease can lead to lower severity of disease and reduce the mortality rate. Arrhythmia is one of the symptoms of cardiovascular disease and cardiovascular complications. ECG signals are used in detection of cardiovascular disease. But this process is very time consuming and can lead to a lot of human errors. Due to strain on the healthcare system this has become an incredibly difficult task. The implementation of machine learning can lead to faster detection of arrhythmia. This will help in early diagnosis and treatment of cardiovascular problems in COVID-19 patients and will lead to good outcomes.

\section{Beneficiaries} \label{sec:beneficiaries}

This system is helpful for medical personnels handling covid-19 cases. This system will also help other patients that suffer from cardiovascular problems or other problems.

The system can be used for a wide range of applications, such as detection of epilepsy from frequency charts obtained during testing, also detection of other disorders. This system will reduce workload from medical staff and allow for better understanding of problems present in patients' cases.

This system can be trained once for generalized predictions, or used for unique purposes depending on users needs. The system does not need machine learning experts to operate, it can be trained and used by end users directly, hence providing an additional layer of security.

\section{Problem Statement} \label{sec:problem_statement}
In current COVID-19 pandemic life threatening complications can be avoided with earlier diagnosis. One of such complications is arrhythmia which can be detected by reading ECG signals. This task is carried out by medical personnel. This repetitive and mundane task puts strain on medical staff.

Supervised learning models can be used for such tasks. These models have their own set advantages and disadvantages. Hence automating selection of the best model for required tasks will allow medical personnel to customise applications based on need. This will reduce strain from medical staff and allow them to focus on patient care.

\section{Scope of the project} \label{sec:scope_of_the_project}

To make the system more efficient, data used for training is provided in csv format. And obtained results are stored in json format. The system handles imputed data with the help of the pandas library. The dataset provided needs to be specific format regardless of length and parameters present in the dataset. The datasets used in this projects are available on kaggle and are converted in required format, but if needed the raw datasets obtained directly from machines can be used for operational purposes.

\section{Organization of Report} \label{sec:organization_of_report}

The report is structure into seven chapters as follows:

\textbf{\textit{Chapter \ref{ch:introduction} - \nameref{ch:introduction}:}}
This chapter gives an overview of the report. It gives a general overview of the current situation of COVID-19 pandemic and the stress it puts on the medical system. It also describes the proposed solution to tackle this problem.

\textbf{\textit{Chapter \ref{ch:literature_survey} - \nameref{ch:literature_survey}:}}
This chapter provides review of relevant literature of supervised learning systems and automation approaches for the model training.

\textbf{\textit{Chapter \ref{ch:system_architecture} - \nameref{ch:system_architecture}:}}
This chapter describes the architecture of the system. It discusses the models used in the system, the automated training and selection of models.

\textbf{\textit{Chapter \ref{ch:system_interface} - \nameref{ch:system_interface}:}}
This chapter describes the user interface of the system. This chapter will discuss the pages accessible by the user and the information about the development server.

\textbf{\textit{Chapter \ref{ch:result_and_analysis} - \nameref{ch:result_and_analysis}:}}
This chapter will describe the performance metrics used by the system for the selection process. The chapter also gives details about the dataset used for training and testing. It also provides recommended system specification required by the application.

\textbf{\textit{Chapter \ref{ch:applications} - \nameref{ch:applications}:}}
This chapter gives various applications of the developed system.

\textbf{\textit{Chapter \ref{ch:conclusion_and_future_scope} - \nameref{ch:conclusion_and_future_scope}:}}
This chapter concludes the report by providing a brief summary of the project. This chapter also describes the future scope of the system.
