\thispagestyle{fancy}
\chapter{Applications} \label{ch:applications}
\section*{\centering Chapter \thechapter}
\section*{\centering Applications}

The application is intended to be used by medical staff in COVID-19 wards. It is primarily built to detect arrhythmia in COVID-19 patients.

\section{Detection of Arrhythmia} \label{sec:detection_of_arrhythmia}
In the early phase of the COVID-19 pandemic, the mortality rate was extremely high. It was partly due to undetected comorbidities in patients. Undetected conditions were the primary cause of severe cases of COVID-19 infection. These conditions were respiratory disorders, cardiovascular disorders, diabetic disorders, etc. Earlier detection of these conditions will help in better case management. The project's application is to detect cardiovascular disorders. For this purpose, the presence of an arrhythmia can be used as a primary sign.

Arrhythmia can be detected from the patient's ECG reports. This process is automated with the application of a supervised learning system. This system allows medical staff to train and select the best-suited model for arrhythmia detection, and help them diagnose such patients. While the primary goal of this project is to be used in COVID-19 cases, it can also be used for regular patients.

\section{Detection of anomalies in medical field} \label{sec:detection_of_anomalies_in_medica_field}
Machine learning is widely used for various tasks in the medical field. Supervised learning is used as diagnosing tool in a few cases. For example, epilepsy is diagnosed by studying scans obtained from the patient's brain. The proposed system can perform an initial screening to detect any anomalies. If such an anomaly is present, it will allow medical personnel to diagnose the patient efficiently.

The application of the system is not limited to diagnosis only, as it can be used for research purposes. These uses are filtering out unwanted data and detecting anomalies. This anomaly detection can be used in research data for discovery purposes. This will increase the productivity of research and lead to rapid development.

\section{Model Training and Predictions} \label{sec:model_training_and_predictions}
The system is capable of training models and selecting models. This system only needs a well-labeled dataset, and it will automatically select the best model for the task. The system can be used by a person without any technical or data science knowledge. The training process can be fine-tuned by adjusting performance weightage. The stored model can be used on similar datasets for prediction purposes.