{\centering \bf \LARGE \scshape
Acknowledgement \\
}

\vspace{1em} \noindent
This dissertation report would not have come into reality without the able guidance, support and wishes of all those who stand by me in the  development. I wish to give my special thanks to my guide, \textbf{Dr. Sushopti Gawade}, for his/her timely advice and guidance.

\noindent
I would like to thank our Principal, \textbf{Dr. Sandeep Joshi} for his constant encouragement throughout the course. I humbly thank our M.E Coordinator, \textbf{Dr. Prashant Nitnaware} and our Head of Department, \textbf{Dr. Satishkumar Verma}, for their valuable guidance \& unending support despite a very busy work schedule. The cheerful spirit they radiated all the time fuelled our desire to excel in the work that I had undertaken.

\noindent
I acknowledge all the staff members of the department of Computer Engineering and department of Information Technology for their help and suggestions during various phases of this project work. It's difficult to forget my eminent supporters that are my Friends and Family members who are always there encouraging me in my every deed.

% \vspace{1em} \noindent
% I remain immensely obliged to \textbf{Dr. Sushopti Gawade}, for providing me with the idea of this topic, and for her invaluable support in garnering resource for me either by way of information or computers also her guidance and supervision which made this seminar happen.

% \noindent
% I would like to thank my college Pillai's Institute of Information Technology, New Panvel, our principal \textbf{Dr. Sandeep Joshi}, M.E. Coordinator \textbf{Dr. Prashant Nitnaware} and the H.O.D. of Information Technology Department \textbf{Dr. Satishkumar Varma} for their invaluable support.

% \noindent
% I would like to say that it has indeed been a fulfilling experience for working on this seminar topic.

\vspace{7.5em}
\begin{flushright}
  \begin{tabular}{c}
    \textbf{Yashodhan Prakash Ketkar} \\
  \end{tabular}
\end{flushright}